%------------------------
% Resume — Haram Lee
% Based on template by Anubhav Singh
%------------------------

\documentclass[letterpaper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Haram Lee}} & \href{https://github.com/rammmaa}{github.com/rammmaa}\\
  +82 10-9273-8240 | \href{mailto:rammma@yonsei.ac.kr}{rammma@yonsei.ac.kr} & \href{https://harammm.me}{harammm.me} \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Yonsei University}{Seoul, South Korea}
      {B.S. in Computer Science, Double Major in Korean Language \& Literature}{Mar. 2024 -- Present}
      \resumeItemListStart
        \item\small{Member of \textbf{YBIGTA}, Yonsei Big Data \& AI Academic Society. \vspace{-2pt}}
        \item\small{Member of \textbf{Molgorithm}, Yonsei Algorithm Problem Solving Club. \vspace{-2pt}}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\vspace{-5pt}
\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Programming Languages}{Python, C++, SQL}
    \resumeSubItem{Frameworks \& Platforms}{React, Electron, Flutter}
    \resumeSubItem{Data Engineering}{Kafka, Flink, Spark, Airflow, Hadoop, DuckDB, ClickHouse}
    \resumeSubItem{Infrastructure \& Cloud}{Docker, AWS (EC2, S3, Lambda, RDS, IAM), Terraform, Nginx}
    \resumeSubItem{Monitoring \& CI/CD}{Grafana, Prometheus, GitHub Actions}
    \resumeSubItem{AI / Robotics}{ROS 2, OpenCV, YOLO}
    \resumeSubItem{Tools}{Git, GitHub, Linux}
    \resumeSubItem{Languages}{Korean (Native), English (Working Proficiency)}
  \resumeSubHeadingListEnd

\vspace{-5pt}
\section{Experience}
  \resumeSubHeadingListStart
    \item \textbf{AI Education Instructor, Osstem Implant} \hfill \textit{Mar. 2026 -- Present}\vspace{-5pt}
      \resumeItemListStart
        \item\small{Delivering AI training program for a cohort of 12 employees at Osstem Implant. \vspace{-2pt}}
      \resumeItemListEnd
    \item \textbf{Freelance Website Maintenance (Next.js)} \hfill \textit{2025 -- Present}\vspace{-5pt}
      \resumeItemListStart
        \item\small{Maintaining and updating a client website built with Next.js on a freelance basis. \vspace{-2pt}}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\vspace{-5pt}
\section{Projects}
  \resumeSubHeadingListStart
    \item \textbf{Compose Coffee Analytics Dashboard} \hfill \textit{Jan. 2026 -- Mar. 2026}\vspace{-5pt}
      \resumeItemListStart
        \item\small{Built components of an internal analytics dashboard for Compose Coffee (YBIGTA industry-academia collaboration) using React, Electron, and DuckDB over normalized POS and delivery-platform data. \vspace{-2pt}}
        \item\small{Automated data normalization workflows across three delivery platforms and POS data, handling roughly 400 million records over a one-year period. \vspace{-2pt}}
      \resumeItemListEnd
    \item \textbf{Real-Time Ride Data Pipeline} \href{https://github.com/YBIGTA/27th-DE-WinterProject}{[Link]} \hfill \textit{Jan. 2026 -- Mar. 2026}\vspace{-5pt}
      \resumeItemListStart
        \item\small{Built a fault-tolerant streaming data pipeline simulating ride data using Kafka and Flink, with real-time ingestion across generator, ingestor, and Flink job services in a containerized environment. \vspace{-2pt}}
        \item\small{Used ClickHouse, Nginx, Terraform, Grafana, and Prometheus for infrastructure, observability, and deployment reliability. \vspace{-2pt}}
      \resumeItemListEnd
    \item \textbf{ROBO-404: AI Hazard Detection Robot} \href{https://github.com/YBIGTA/27th-conference-robo404}{[Link]} \hfill \textit{Sep. 2025 -- Mar. 2026}\vspace{-5pt}
      \resumeItemListStart
        \item\small{Developed an AI-powered hazard detection robot system using ROS 2 and YOLO for real-time environmental perception, integrating computer vision and robotics components for responsive hazard recognition. \vspace{-2pt}}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\vspace{-5pt}
\section{Honors and Awards}
\begin{description}[font=$\bullet$]
  \item {RC House Outstanding Program Award \hfill Dec. 2025}
  \vspace{-5pt}
  \item {Encouragement Prize, \textbf{Upstage LLM Query Hackathon} (Team 22:34) \hfill Nov. 2025}
  \vspace{-5pt}
  \item {Grand Prize, \textbf{RC Portfolio Competition} \hfill Jul. 2024}
\end{description}

\vspace{-5pt}
\section{Leadership and Activities}
  \resumeSubHeadingListStart
    \resumeSubheading
      {YBIGTA \textnormal{\href{https://github.com/YBIGTA}{[Link]}}}{Jun. 2025 -- Present}
      {Data Engineering Member, Executive Board}{Yonsei Big Data \& AI Academic Society}
    \resumeSubheading
      {Molgorithm \textnormal{\href{https://github.com/yonsei-molgorithm}{[Link]}}}{Mar. 2025 -- Present}
      {Executive}{Yonsei Algorithm Problem Solving Club}
    \resumeSubheading
      {ICPC Sinchon \textnormal{\href{https://github.com/icpc-sinchon}{[Link]}}}{Apr. 2025 -- Feb. 2026}
      {Staff (Spring 2025), Camp Director (Winter 2026)}{Inter-university competitive programming community}
    \resumeSubheading
      {Residential Assistant}{Mar. 2025 -- Dec. 2025}
      {Yonsei International Campus, Muak House}{}
    \resumeSubheading
      {CS Student Council}{Apr. 2024 -- Dec. 2025}
      {Executive}{Yonsei University Computer Science Department Student Council}
  \resumeSubHeadingListEnd

\end{document}
